Sound and Automated Synthesis of Digital Controllers for Physical Plants

### 2016-10-06 paper/paper.tex
hscc17

@@

Using an optimization tool, Wang {\it et
al.}~\cite{DBLP:conf/hybrid/WangGRJF16} design a high-performance
controller, which is characterized by the following z-expression:

\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}

The authors claim that this controller $C(z)$ is extremely stable for the
discrete plant model $G(z)$.  However, if implementation aspects are
considered during verification, this controller becomes unstable.

For this particular example, the actual implementation of $C(z)$ using
\param{4}{16} implementation format can be represented by the following
z-expression:

\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
}
\end{equation}

\noindent which makes the system unstable in closed-loop using the typical series loop configuration.

>>>>

\blue{[Perhaps we should anticipate this example, partly showing potential repercussions of our formal approach. 
Indeed, this example does not show the full potential, since it does not start with the physical plant $G(s)$. ]}

@@

Using an optimisation tool, 
the work in~\cite{DBLP:conf/hybrid/WangGRJF16} has designed a high-performance controller that is characterised by the following z-domain transfer function:
\begin{equation}
\label{Eq:running-example-controller}
C\left(z\right) := \frac{2.72z^2 - 4.153z + 1.896}{z^2 - 1.844z + 0.8496}.
\end{equation}
The authors claim that this controller $C(z)$ is extremely stable for the discrete plant model $G(z)$.  
However, if \red{[which ones? quantisation?] implementation aspects} are considered during verification, 
this controller becomes unstable.
%
Indeed, the actual implementation of $C(z)$ using \param{4}{16} \red{[clarify this notation]} 
implementation format can be represented by the following expression: 
\begin{equation}
\label{Eq:running-example-controller-quantized}
\resizebox{0.5\textwidth}{!}{
$C_{q}\left(z\right) {:=} \frac{2.7199859619140625z^2{-}4.1529998779296875z
{+}1.89599609375}{z^2{-}1.843994140625z+0.8495941162109375},$
}
\end{equation} 
which makes the system unstable in closed-loop \red{using the typical series loop configuration [meaning?]}.
